\chapter{Exercise 00}
\input{exercises/en.ex00_interlude.tex}
\newpage
\extitle{Multivariate Hypothesis - Iterative Version}
\turnindir{ex00}
\exnumber{00}
\exfiles{prediction.py}
\exforbidden{None}
\makeheaderfilesforbidden

% ================================== %
\section*{Objective}
% ---------------------------------- %
Manipulate the hypothesis to make a prediction.\\
\newline
You must implement the following formula as a function:

$$
\begin{matrix}
  \hat{y}^{(i)} = \theta_0 + \theta_1 x_{1}^{(i)}  + \dots + \theta_n x_{n}^{(i)} && & \text{ for i = 1, ..., m}
\end{matrix}
$$
Where:
\begin{itemize}
  \item $\hat{y}$ is a vector of dimension $m$: the vector of predicted values
  \item $\hat{y}^{(i)}$ is the i$^\text{th}$ component of the $\hat{y}$ vector: the predicted value for the i$^\text{th}$ example
  \item $\theta$ is a vector of dimension $(n + 1)$: the parameter vector
  \item $\theta_j$ is the j$^\text{th}$ component of the parameter vector
  \item $X$ is a matrix of dimensions $(m \times n)$: the design matrix
  \item $x^{(i)}$ is the i$^\text{th}$ row of the $X$ matrix: the feature vector of the i$^\text{th}$ example
  \item $x_{j}$ is the j$^\text{th}$ column of the $X$ matrix
  \item $x_j^{(i)}$ is the element at the intersection of the i$^\text{th}$ row and the j$^\text{th}$ column of the $X$ matrix: the j$^\text{th}$ feature of the i$^\text{th}$ example
\end{itemize}
\newpage
% ================================== %
\section*{Instructions}
% ---------------------------------- %

In the \texttt{prediction.py} file, create the following function as per the instructions given below:\\
\newline
\par
\begin{minted}[bgcolor=darcula-back,formatcom=\color{lightgrey},fontsize=\scriptsize]{python}
  def simple_predict(x, theta):
      """Computes the prediction vector y_hat from two non-empty numpy.array.
      Args:
        x: has to be an numpy.array, a matrix of dimension m * n.
        theta: has to be an numpy.array, a vector of dimension (n + 1) * 1.
      Return:
        y_hat as a numpy.array, a vector of dimension m * 1.
        None if x or theta are empty numpy.array.
        None if x or theta dimensions are not matching.
        None if x or theta is not of expected type.
      Raises:
        This function should not raise any Exception.
      """
      ... Your code ...
\end{minted}

% ================================== %
\section*{Examples}
% ---------------------------------- %

\begin{minted}[bgcolor=darcula-back,formatcom=\color{lightgrey},fontsize=\scriptsize]{python}
import numpy as np
x = np.arange(1,13).reshape((4,-1))

# Example 1:
theta1 = np.array([5, 0, 0, 0]).reshape((-1, 1))
simple_predict(x, theta1)
# Ouput:
array([[5.], [5.], [5.], [5.]])
# Do you understand why y_hat contains only 5's here?  


# Example 2:
theta2 = np.array([0, 1, 0, 0]).reshape((-1, 1))
simple_predict(x, theta2)
# Output:
array([[ 1.], [ 4.], [ 7.], [10.]])
# Do you understand why y_hat == x[:,0] here?  


# Example 3:
theta3 = np.array([-1.5, 0.6, 2.3, 1.98]).reshape((-1, 1))
simple_predict(x, theta3)
# Output:
array([[ 9.64], [24.28], [38.92], [53.56]])


# Example 4:
theta4 = np.array([-3, 1, 2, 3.5]).reshape((-1, 1))
simple_predict(x, theta4)
# Output:
array([[12.5], [32. ], [51.5], [71. ]])
\end{minted}