\chapter{Exercise 01}
\input{exercises/en.ex01_interlude.tex}
\newpage
\extitle{Multivariate hypothesis - vectorized version}
\turnindir{ex01}
\exnumber{01}
\exfiles{prediction.py}
\exforbidden{None}
\makeheaderfilesforbidden

% ================================= %
\section*{Objective}
% --------------------------------- %
Manipulate the hypothesis to make a prediction.\\
\newline
You must implement the following formula as a function:  

$$
\hat{y} = X' \cdot \theta = 
\begin{bmatrix} 
1 & x_{1}^{(1)} & \dots & x_{n}^{(1)}\\
\vdots & \vdots & \ddots & \vdots\\
1 & x_{1}^{(m)} & \dots &  x_{n}^{(m)}\end{bmatrix}
\cdot
\begin{bmatrix}
\theta_0 \\ 
\theta_1 \\
\vdots \\
\theta_n
\end{bmatrix} 
= 
\begin{bmatrix} 
\theta_0 + \theta_{1} x_{1}^{(1)} + \dots + \theta_{n} x_{n}^{(1)}\\ 
\vdots \\ 
\theta_0 + \theta_{1} x_{1}^{(m)} + \dots + \theta_{n} x_{n}^{(m)}
\end{bmatrix}
$$
Where:
\begin{itemize}
  \item $\hat{y}$ is a vector of dimension $m$: the vector of predicted values
  \item $X$ is a matrix of dimensions $(m \times n)$: the design matrix
  \item $X'$ is a matrix of dimensions $(m \times (n + 1))$: the design matrix onto which a column of $1$'s was added as a first column
  \item $\theta$ is a vector of dimension $(n + 1)$: the parameter vector
  \item $x^{(i)}$ is the i$^\text{th}$ row of the $X$ matrix
  \item $x_{j}$ is the j$^\text{th}$ column of the $X$ matrix
  \item $x_j^{(i)}$ is the intersection of the i$^\text{th}$ row and the j$^\text{th}$ column of the $X$ matrix: the j$^\text{th}$ feature of the i$^\text{th}$ training example.
\end{itemize}
Be careful: 
\begin{itemize}
  \item The \texttt{x} argument your function will receive as an input corresponds to $X$, the $(m \times n)$ matrix.
        Not $X'$.
  \item \texttt{theta} is an $(n + 1)$ vector.
  \item You have to transform \texttt{x} to fit \texttt{theta}'s dimensions
\end{itemize}
\newpage
% ================================= %
\section*{Instructions}
% --------------------------------- %
In the \texttt{prediction.py} file, write the \texttt{predict\_} function as per the instructions given below:

\begin{minted}[bgcolor=darcula-back,formatcom=\color{lightgrey},fontsize=\scriptsize]{python}
def predict_(x, theta):
    """Computes the prediction vector y_hat from two non-empty numpy.array.
    Args:
      x: has to be an numpy.array, a vector of dimensions m * n.
      theta: has to be an numpy.array, a vector of dimensions (n + 1) * 1.
    Return:
      y_hat as a numpy.array, a vector of dimensions m * 1.
      None if x or theta are empty numpy.array.
      None if x or theta dimensions are not appropriate.
      None if x or theta is not of expected type.
    Raises:
      This function should not raise any Exception.
    """
    ... Your code ...
\end{minted}

% ================================= %
\section*{Examples}
% --------------------------------- %

\begin{minted}[bgcolor=darcula-back,formatcom=\color{lightgrey},fontsize=\scriptsize]{python}
import numpy as np
x = np.arange(1,13).reshape((4,-1))

# Example 1:
theta1 = np.array([5, 0, 0, 0]).reshape((-1, 1))
predict_(x, theta1)
# Ouput:
array([[5.], [5.], [5.], [5.]])
# Do you understand why y_hat contains only 5's here?  

# Example 2:
theta2 = np.array([0, 1, 0, 0]).reshape((-1, 1))
predict_(x, theta2)
# Output:
array([[ 1.], [ 4.], [ 7.], [10.]])
# Do you understand why y_hat == x[:,0] here?  


# Example 3:
theta3 = np.array([-1.5, 0.6, 2.3, 1.98]).reshape((-1, 1))
predict_(x, theta3)
# Output:
array([[ 9.64], [24.28], [38.92], [53.56]])


# Example 4:
theta4 = np.array([-3, 1, 2, 3.5]).reshape((-1, 1))
predict_(x, theta4)
# Output:
array([[12.5], [32. ], [51.5], [71. ]])
\end{minted}