\chapter{Exercise 10}
\extitle{Machine Learning for Grown-ups: Trantor guacamole business}
\turnindir{ex10}
\exnumber{10}
\exfiles{space\_avocado.py, benchmark\_train.py,  models.[csv/yml/pickle]}
\exforbidden{sklearn}
\makeheaderfilesforbidden

% ================================= %
\section*{Objective}
% --------------------------------- %
Let's do Machine Learning for "real"!

% ================================= %
\section*{Introduction}
% --------------------------------- %
The dataset is made of 5 columns:
\begin{itemize}
  \item \textbf{index}: not relevant
  \item \textbf{weight}: the avocado weight order (in tons)
  \item \textbf{prod\_distance}: distance from where the avocado ordered is produced (in Mkm)
  \item \textbf{time\_delivery}: time between the order and the receipt (in days)
  \item \textbf{target}: price of the order (in trantorian unit)
\end{itemize}
It contains the data of all the avocado purchases made by Trantor administration (guacamole is a serious business there).
\newpage
% ================================= %
\section*{Instructions}
% --------------------------------- %
You have to explore different models and select the best you find.\\
\newline
To do this:
\begin{itemize}
  \item Split your \texttt{space\_avocado.csv} dataset into a training and a test set.
  \item Use your \texttt{polynomial\_features} method on your training set.
  \item Consider several Linear Regression models with polynomial hypothesis with a maximum degree of 4.
  \item Evaluate your models on the test set.
\end{itemize}

According to your model evaluations, what is the best hypothesis you can get?
\begin{itemize}
  \item Plot the evaluation curve which help you to select the best model (evaluation metrics vs models).
  \item Plot the true price and the predicted price obtained via your best model (3D representation or 3 scatterplots).
\end{itemize}

The training of all your models can take a long time.\\
\\
Thus you need to train only the best one during the correction.\\
\\
But, you should return in \texttt{benchmark\_train.py} the program which performs the training of all the models and save the parameters of the different models into a file.\\
\\
In \texttt{models.[csv/yml/pickle]} one must find the parameters of all the models you have explored and trained.\\
\\
In \texttt{space\_avocado.py} train the model based on the best hypothesis you find and load the other models from \texttt{models.[csv/yml/pickle]}.\\
\newline
Then evaluate and plot the different graphics as asked before.