\chapter{Exercise 06}
\extitle{Normalization II: Min-max Standardization}
\turnindir{ex06}
\exnumber{06}
\exfiles{minmax.py}
\exforbidden{None}
\makeheaderfilesforbidden


% ================================= %
\section*{Objective}
% --------------------------------- %
Introduction to standardization/normalization methods.
Implement another normalization method.\\
\\
You must implement the following formula as a function: 

$$
\begin{matrix}
  x'^{(i)} = \frac{x^{(i)} - min(x)}{max(x) - min(x)} & & \text{ for $i = 1, ..., m$}
\end{matrix}
$$
Where:
\begin{itemize}
  \item $x$ is a vector of dimension $m$
  \item $x^{(i)}$ is the i$^\text{th}$ component of vector $x$
  \item $min(x)$ is the minimum value found among the components of vector $x$
  \item $max(x)$ is the maximum value found among the components of vector $x$
\end{itemize}
You will notice that this min-max standardization doesn't scale the values to the $[-1,1]$ range.
What do you think the final range will be?
\newpage
% ================================= %
\section*{Instructions}
% --------------------------------- %
In the \texttt{minmax.py} file, create the \texttt{minmax} function as per the instructions given below:\\
\begin{minted}[bgcolor=darcula-back,formatcom=\color{lightgrey},fontsize=\scriptsize]{python}
def minmax(x):
	"""Computes the normalized version of a non-empty numpy.ndarray using the min-max standardization.
	Args:
		x: has to be an numpy.ndarray, a vector.
	Returns:
		x' as a numpy.ndarray. 
		None if x is a non-empty numpy.ndarray or not a numpy.ndarray.
	Raises:
		This function shouldn't raise any Exception.
	"""
    ... Your code ...
\end{minted}

% ================================= %
\section*{Examples}
% --------------------------------- %
\begin{minted}[bgcolor=darcula-back,formatcom=\color{lightgrey},fontsize=\scriptsize]{python}
# Example 1:
X = np.array([0, 15, -9, 7, 12, 3, -21]).reshape((-1, 1))
minmax(X)
# Output:
array([0.58333333, 1.        , 0.33333333, 0.77777778, 0.91666667,
		0.66666667, 0.        ])

# Example 2:
Y = np.array([2, 14, -13, 5, 12, 4, -19]).reshape((-1, 1))
minmax(Y)
# Output:
array([0.63636364, 1.        , 0.18181818, 0.72727273, 0.93939394,
		0.6969697 , 0.        ])
\end{minted}