\chapter{Exercise 01}
\extitle{L2 Regularization}
\input{exercises/en.ex01_interlude.tex}
\newpage
\turnindir{ex01}
\exnumber{01}
\exfiles{l2\_reg.py}
\exforbidden{sklearn}
\makeheaderfilesforbidden

% ================================= %
\section*{Objective}
% --------------------------------- %
You must implement the following formulas as functions:  

% ================================= %
\subsection*{Iterative}
% --------------------------------- %
$$
L_2(\theta)^2 = \sum_{j = 1}^n \theta_j^2
$$
\\
Where:
\begin{itemize}
  \item $\theta$ is a vector of dimension $(n + 1)$.
\end{itemize}

% ================================= %
\subsection*{Vectorized}
% --------------------------------- %
$$
L_2(\theta)^2 = \theta' \cdot \theta'
$$
\\
Where:
\begin{itemize}
  \item $\theta'$ is a vector of dimension $(n + 1)$, constructed using the following rules:
\end{itemize}
  
$$
\begin{matrix}
\theta'_0 & =  0 \\
\theta'_j & =  \theta_j & \text{ for } j = 1, \dots, n\\
\end{matrix}
$$
\newpage
% ================================= %
\section*{Instructions}
% --------------------------------- %
In the \texttt{l2\_reg.py} file, write the following functions as per the instructions given below:\\
\\
\begin{minted}[bgcolor=darcula-back,formatcom=\color{lightgrey},fontsize=\scriptsize]{python}
def iterative_l2(theta):
	"""Computes the L2 regularization of a non-empty numpy.ndarray, with a for-loop.
	Args:
		theta: has to be a numpy.ndarray, a vector of shape n * 1.
	Returns:
		The L2 regularization as a float.
		None if theta in an empty numpy.ndarray.
	Raises:
		This function should not raise any Exception.
	"""
	... Your code ...

def l2(theta):
	"""Computes the L2 regularization of a non-empty numpy.ndarray, without any for-loop.
	Args:
		theta: has to be a numpy.ndarray, a vector of shape n * 1.
	Returns:
		The L2 regularization as a float.
		None if theta in an empty numpy.ndarray.
	Raises:
		This function should not raise any Exception.
	"""
	... Your code ...
\end{minted}

% ================================= %
\section*{Examples}
% --------------------------------- %

\begin{minted}[bgcolor=darcula-back,formatcom=\color{lightgrey},fontsize=\scriptsize]{python}
x = np.array([2, 14, -13, 5, 12, 4, -19]).reshape((-1, 1))

# Example 1: 
iterative_l2(x)
# Output:
911.0

# Example 2: 
l2(x)
# Output:
911.0

y = np.array([3,0.5,-6]).reshape((-1, 1))
# Example 3: 
iterative_l2(y)
# Output:
36.25

# Example 4: 
l2(y)
# Output:
36.25
\end{minted}