\chapter{Exercise 00}
\input{exercises/en.ex00_interlude.tex}
\newpage
\extitle{Sigmoid}
\turnindir{ex00}
\exnumber{00}
\exfiles{sigmoid.py}
\exforbidden{None}
\makeheaderfilesforbidden

% ================================== %
\section*{Objective}
% ---------------------------------- %
Introduction to the hypothesis in the context of logistic regression.\\
\\
You must implement the sigmoid function, given by the following formula:

$$
\text{sigmoid}(x) = \cfrac{1} {1 + e^{-x}}
$$
Where:
\begin{itemize}
  \item $x$ is a scalar or a vector,
  \item $e$ is the contracted form for the exponential function. It is also a mathematical constant, named Euler's number.
\end{itemize}
This function is also known as \textbf{Standard logistic sigmoid function}.
This explains the name \textit{logistic regression}.\\
\\
The sigmoid function transforms an input into a probability value, i.e. a value between 0 and 1.  
This probability value will then be used to classify the inputs.
\\
% ================================== %
\section*{Instructions}
% ---------------------------------- %
In the \texttt{sigmoid.py} file, write the following function as per the instructions below:\\
\\
\par
\begin{minted}[bgcolor=darcula-back,formatcom=\color{lightgrey},fontsize=\scriptsize]{python}
def sigmoid_(x):
    """
    Compute the sigmoid of a vector.
    Args:
        x: has to be a numpy.ndarray of shape (m, 1).
    Returns: 
        The sigmoid value as a numpy.ndarray of shape (m, 1).
        None if x is an empty numpy.ndarray.
    Raises:
        This function should not raise any Exception.
    """
    ... Your code ...
\end{minted}

% ================================== %
\section*{Examples}
% ---------------------------------- %

\begin{minted}[bgcolor=darcula-back,formatcom=\color{lightgrey},fontsize=\scriptsize]{python}
# Example 1:
x = np.array([[-4]])
sigmoid_(x)
# Output:
array([[0.01798620996209156]])

# Example 2:
x = np.array([[2]])
sigmoid_(x)
# Output:
array([[0.8807970779778823]])

# Example 3:
x = np.array([[-4], [2], [0]])
sigmoid_(x)
# Output:
array([[0.01798620996209156], [0.8807970779778823], [0.5]])
\end{minted}


\info{
  Our sigmoid formula is a special case of the logistic function below, with $L = 1$, $k = 1$ and $x_0 = 0$:
  $$
  f(x) = \cfrac{L}{1 + e^{-k(x-x_0)}}
  $$
}