%******************************************************************************%
%                                                                              %
%                                 Interlude                                    %
%                         for Machine Learning module                          %
%                                                                              %
%******************************************************************************%

% ============================================== %
\section*{One Last Word - It's Just a Beginning...}
% ============================================== %
\subsection*{Congratulation!!}
% ---------------------------------------------- %
You have finished this bootcamp and you can be proud of yourself!
We hope you liked it and that the material were understandable.

We tried our best to make it as accessible as possible to anyone, even for someone with little mathematical background. It was quite a challenge, and we hope we succeed to that difficult mission.

Equiped with your brand-new knowledge you are now able to tackle more challenging algorithm like \texttt{\textbf{ensemble methods (random forest, gradient boosting)}}, \texttt{\textbf{support vector machine}} or even \texttt{\textbf{artificial neural networks}}!!

An because we know that \texttt{\textbf{a lot of you have neural networks in mind}} when you started this journey into machine learning, let's talk a bit more about why you are now able to deep dive into it... fearlessly!

\texttt{\textbf{Neural networks}} are based on the same blocks you should now be familiar with.
Essentially:
\begin{itemize}
      \item matrix and vector operations,
      \item gradient descent,
      \item regularization,
      \item sigmoid (as activation functions, even if it is a bit outdated now)
\end{itemize}

Let's see what you can do now.

% ============================================== %
\subsection*{To go further}
% ---------------------------------------------- %
To keep learning Machine Learning, here are several options you should consider:
\begin{itemize}
      \item To complete the entire \href{https://www.coursera.org/learn/machine-learning/home/}{Stanford's Machine Learning MOOC}.
            It is a great ressource, a \textbf{classic} for those who want to study machine learning.
            This bootcamp followed thigthly the architecture of its first three weeks.
            This course is definitely worth your time!
            Also, someone did a great work to convert all the Octave assignments into \href{https://github.com/dibgerge/ml-coursera-python-assignments}{Python notebooks}.
      \item To take \href{https://course.fast.ai/}{fast.ai Deep Learning MOOC}.
            It's a great way to learn Deep Learning following a top-down approach.
\end{itemize}